---
title: "Project 1"
output:
  html_document:
    df_print: paged
---
My main interest in to explore the most common auther and his sentences in the dataset. Relating areas of articles to explore may have: the key words of contents, the most common ending punctuation and the sentence length analysis, the relationship between of the original publcation date and the corpus publication date.
```{r}
library(dplyr)
library(ds4psy)
library(ggplot2)
```

```{r}
setwd("C:\\Users\\tuyum\\Desktop\\study\\Columbia\\Applied DS")
data<-read.csv("philosophy_data.csv")
summary(data)
```
From the summary, we can take a glance at the distribution of original publication date, corpus edition date and sentence length. By looking at the min, max, mean, we can have a general idea of the range and frequency.
```{r}
glimpse(data)
```
I

```{r}
table(data$author)
```
II

So from the table of authers' frequency we can see that, Aristotle had the most articles (48779) collected in out dataset.Meanwhile, Wollstonecraft has the least (2559).

```{r}
Subset<-filter(data,author=="Aristotle")
freq <- sort(table(unlist(strsplit(toString(Subset$sentence_spacy), " "))),
               decreasing = TRUE)
freq[1:100]
```
So we see that most of the words of top 100 frequency in Aristotle's sentences are actually general prepositions. However, except the prepositioons, there are some interesting words with high frequency such as one (8120), two (2009) and time(1566). This may bring us the think that Aristotle, as a philosopher, discussed a lot about human as single independent and as one end of dualistic relationship. Also, the words time reveals a topic that has been trending all the time among the philosopgers.
```{r}
end1=0   ## sum the number of "."
end2=0   ## sum the number of "!"
end3=0   ## sum the number of "?"
c1=c()    ## track the location of sentences end with"." and store the sentence length
c2=c()    ## track the location of sentences end with"!" and store the sentence length
c3=c()    ## track the location of sentences end with"?" and store the sentence length
for (i in 1:360808)
  {
    e<-unlist(strsplit(toString(Subset$sentence_spacy[i]), " "))
    l<-length(e)
    end1=end1+as.numeric(endsWith(e[l],"."))
    end2=end2+as.numeric(endsWith(e[l],"!"))
    end3=end3+as.numeric(endsWith(e[l],"?"))
    if (endsWith(e[l],".")==TRUE)
      {
        c1<-append(c1,Subset$sentence_length[i])
      }
    if (endsWith(e[l],"!")==TRUE)
      {
        c2<-append(c2,Subset$sentence_length[i])
      }
    if (endsWith(e[l],"?")==TRUE)
      {
        c3<-append(c3,Subset$sentence_length[i])
      }
}
end1
end2
end3
```
There are 41849 sentences ending with ".", 14 sentences ending with "!", and 3303 sentences ending with "?" in Aritotle's collected sentences. Now let us analyze if the lengths of sentences are related to these ending punctuations.
```{r}
mean(c1)
mean(c2)
mean(c3)
```
Hence, we see that the sentences ending with "." tend to be longer than others. The sentences ending with "?" tend to be shorter than others. For the ones ending with "!", since there are only 14 sentences, I would rather not trust the result too much since the observations are not enough, at least not at the level of the observations for the other two. Let us visualize the three arrays:
```{r}
plot(c1)
plot(c2)
plot(c3)
```
III

Finally, I want to analyze the relationship between original publcation date and the corpus publication date. We are sure that the corpus publication date is later than the original publication date, but how late?
```{r}
x<-na.omit(Subset$original_publication_date)
y<-na.omit(Subset$corpus_edition_date)
head(x)
head(y)
mean(x)
mean(y)
```
I suspect that every date in x is -320 and in y is 1991. Let us test.
```{r}
check_x=TRUE
for (i in 1:length(x)){
  x[i]!=-320
  check_x==FALSE
}
check_y=TRUE
for (i in 1:length(y)){
  y[i]!=-1991
  check_y==FALSE
}
check_x
check_y
```

Thus, we comfirm that every sentence of Aritotle in this data was originally published in -320 and corpusly published in 1991. Due to the lack of variablity, we are unable to test the relationship between the two dates. Consider to do this relationship check among another subset which contains multiple authers.  



